Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
use count data directly

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent across land cover resolutions
in forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
decreasing in foraging habitat (23.9% at 30 m - <2% at 1000 m).  <!-- TODO: 
break up -->Overall, these
results indicate the importance of matching land cover resolution to scale of
habitat selection as well as ensuring the land cover product used has a resolution fine
enough to detect landscape features and habitats relevant to study species, such
as important patchy and rare habitats.

>>>>

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent across land cover resolutions
in forest and open layers (Figure \@ref(fig:lcres) D). Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
with increasing spatial resolution, while decreasing in foraging habitat 
(`r count[res == 30 & lc == 3, percent]`% at 30 m
- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
indicate the importance of matching land cover resolution to scale of
habitat selection and choosing a land cover product with a resolution
sufficient to detect less common habitats.
